%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Applied Scientist Intern} % Job title
    {Amazon Lex Team} % Organization
    {Seattle, U.S. (Remote) } % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research on applying a new method which have good performance on CV dataset to NLP tasks. Related to online learning and transfer learning.}
      \end{cvitems}
    }
    
  \cventry
    {Machine Learning Engineer} % Job title
    {RSVP.ai} % Organization
    {Waterloo, Canada} % Location
    {Sept. 2019 - June. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented paraphrase generation models and conduced human evaluation for paraphrase evaluation.}
        \item {Conducted human labeling experiment comparing different models and confirm the effectiveness of BLEU evaluation.}
        \item {Improve question answering system with paraphrase-augmented queries and named-entity-filtered examples.}
      \end{cvitems}
    }
 
 \cventry
    {Machine Learning Engineer}
    {RSVP.ai}% Job title
    {Waterloo, Canada} % Location
    {Dec. 2018 - Sept 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed an end-to-end question answering system that integrates BERT (\textbf{Tensorflow}) with the open-source Anserini (a \textbf{Lucene} IR toolkit) information retrieval toolkit both in English and Chinese and create new state of the art.}
	\item {Tested the system's performance with \textbf{Elastic Search API} and provided real-time online service.}
        \item {Applied the system to domain specific document information retrieval.}
      \end{cvitems}
    }
 
\cventry
    {Machine Learning Algorithm Intern} % Job title
    {Yitu-Tech} % Organization
    {Shanghai, China} % Location
    {Feb. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Worked on the car detection project.}
        \item {Improved the \textbf{Single Shot MultiBox Detector} model for object detection on car detection task.}
        \item {Implemented the HOG-SVM for digital recognition in car license detection.}
      \end{cvitems}
    }
        
\end{cventries}
